Put Title here

### 2018-10-30 General WLD combinatorics.tex
some changes while talking

\begin{dfn}\label{equivdfn} \todo{I feel like I need some sort of uniqueness of partition result to even be able to define this well. Or something. Can we discuss?}
There is an equivalence relationship on the set of admissible Wilson loops diagrams generated by the following binary relation: $W = (\cP, n) \sim W'= (\cP', n)$ if
\begin{enumerate}
\item There exist two different exact subdiagrams, $(P, V(P))$ and $(P', V(P'))$ of $W$ and $W'$ respectively such that $V(P) =  V(P')$.
\item The complementary subdiagrams are identical: $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.
\end{enumerate}
\end{dfn}

@@

\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon partitions in Example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ are maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$. The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition. \note{do we want a picture of a dual tree here? Being lazy}
\end{eg}

@@

Let $T(W)$ be the dual graph of $\tau(W)$ with the vertex corresponding to the infinite face split.
%In other words, place a vertex on each finite face of $\tau(W)$. These vertices are connected if there is a chord edge separating the edges. Furthermore, if the face is bounded by an edge of the polygonal cycle of $\tau(W)$, the corresponding vertex gets a leaf edge for each such boundary.
Since $\tau(W)$ is an embedded graph (with a fixed distinguished embedding) by Lemma \ref{tausimpleplanarlem}, $T(W)$ is an uniquely defined graph.\note{The fixed embedding is important, because otherwise you only have a unique planar dual if the graph is 3-connected which this one isn't.  I'm just noting that here so that everyone knows why I added the part about the embedding and then we can take this comment out.}

>>>>

\begin{dfn}\label{equivdfn} 
There is an equivalence relationship on the set of admissible Wilson loops diagrams given by the transititve closure the following binary relation: $W = (\cP, n) \sim W'= (\cP', n)$ if
\begin{enumerate}
\item There exist two different exact subdiagrams, $(P, V(P))$ and $(P', V(P'))$ of $W$ and $W'$ respectively such that $V(P) =  V(P')$.
\item The complementary subdiagrams are identical: $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.
\end{enumerate}
\end{dfn}

@@

\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon partitions in Example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ are maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$. The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition. \note{Put a picture of a dual tree.  Make a comment that the embedding is required to obtain uniqueness of the dual}
\end{eg}

@@

Let $T(W)$ be the dual graph of $\tau(W)$ with the vertex corresponding to the infinite face split.
%In other words, place a vertex on each finite face of $\tau(W)$. These vertices are connected if there is a chord edge separating the edges. Furthermore, if the face is bounded by an edge of the polygonal cycle of $\tau(W)$, the corresponding vertex gets a leaf edge for each such boundary.
Since $\tau(W)$ is an embedded graph (with a fixed distinguished embedding) by Lemma \ref{tausimpleplanarlem}, $T(W)$ is an uniquely defined graph.
